Implementing DNS in C0

### 2017-11-16 proposal.tex
add project.bib for local bibliographic entries
add some bibliography entries
discuss related work

\documentclass{article}
\usepackage[tt=false]{libertine}
\usepackage{mathpartir}
\usepackage{amsthm}
\usepackage[colorlinks=true]{hyperref}
\usepackage{bytefield}
%\usepackage{fullpage}
\usepackage{listings}

@@

\newcommand\Lang[1]{{\sffamily\bfseries{#1}}}
\newcommand\LangCA{\Lang{CA}}
\newcommand\LangMA{\Lang{MA}}
\newcommand\EOf[4]{{#1}\vdash_{#2}{#3}:{#4}}
\newcommand\MOf[4]{{#1}\vdash_{#2}{#3}\div{#4}}
\newcommand\IsProc[3]{{#1}\vdash_{#2}{#3}\ \mathsf{proc}}
\newcommand\IsAction[3]{{#1}\vdash_{#2}{#3}\ \mathsf{action}}

@@

\subsection{Related Work}
Jon.

@@

Our original project proposal was to develop a language for safe
concurrent programming with precise formal guarantees; however, the
negotiation process led us to choose a completely unrelated project,
which we describe in this section. We will be developing an
implementation of the DNS protocol in the memory-safe \Lang{C0}
language (see \S\ref{sec:c0}); we have divided our work into two
principle components.

@@

Unlike \Lang{C}, the \Lang{C0} language has only a single type of
integers, which are represented internally as 32-bit integers. The
network interface (see \S\ref{sec:network-interface}) will deal with
requests and responses formatted as arrays of 32-bit integers; it is
the responsibility of the marshalling-and-unmarshalling module to
unpack this data into structured representations of core DNS
datatypes.

@@

typedef struct resource_record* resource_record_t;
  \end{lstlisting}
  \caption{Example DNS data structures in our \Lang{C0} implementation.}\label{fig:c0-data-structures}
\end{figure}

For instance, Figure~\ref{fig:layout-message-header} shows the
bit-level layout of DNS message headers, and
Figure~\ref{fig:layout-resource-record} shows the same for resource
records; Figure~\ref{fig:c0-data-structures} shows how we code these
structures in our \Lang{C0} implementation. To convert between these
structured representations and the sequences of words which are used
at the boundaries of the network
interface~(\S\ref{sec:network-interface}), we implement functions of
the following kind:

@@

\bibliographystyle{abbrv}
\bibliography{bibtex-references/refs}

>>>>

\documentclass{article}
\usepackage[tt=false]{libertine}
\usepackage{mathpartir}
\usepackage{amsthm}
\usepackage[colorlinks=true]{hyperref}
\usepackage{bytefield}
%\usepackage{fullpage}
\usepackage{listings}
\usepackage{microtype}

@@

\newcommand\Kwd[1]{{\sffamily\bfseries{#1}}}
\newcommand\EOf[4]{{#1}\vdash_{#2}{#3}:{#4}}
\newcommand\MOf[4]{{#1}\vdash_{#2}{#3}\div{#4}}
\newcommand\IsProc[3]{{#1}\vdash_{#2}{#3}\ \mathsf{proc}}
\newcommand\IsAction[3]{{#1}\vdash_{#2}{#3}\ \mathsf{action}}

@@

\subsection{Related Work}

\paragraph{The \Kwd{Fox} Project}
An earlier example of an implementation of the DNS protocol in a safe
and formally specified language is given by the \Kwd{Fox} project,
undertaken at Carnegie Mellon University in the
1990s~\cite{biagioni-harper-lee-milnes:1994,
  biagioni-harper-lee:2001}. Their principal artifact was a library
called \Kwd{FoxNet} which implemented an array of low-level network
infrastructure, including \Kwd{TCP}, \Kwd{IP}, \Kwd{ARP} and \Kwd{DNS}
in the \Kwd{Standard ML} language.

Unlike our development, \Kwd{FoxNet} had a highly modular character
which was enabled by the host language's sophisticated module system
(at the time, the only language to support signatures, structures and
generative functors, which are crucial for safe abstraction).

\paragraph{Other implementations} More recently, safe languages like
\Kwd{Rust} and \Kwd{Go} have been gaining popularity. Both languages
have hosted implementations of the \Kwd{DNS}
protocol~\cite{github:trust-dns,github:miekg-dns}

@@

Our original project proposal was to develop a language for safe
concurrent programming with precise formal guarantees; however, the
negotiation process led us to choose a completely unrelated project,
which we describe in this section. We will be developing an
implementation of the DNS protocol in the memory-safe \Kwd{C0}
language (see \S\ref{sec:c0}); we have divided our work into two
principle components.

@@

Unlike \Kwd{C}, the \Kwd{C0} language has only a single type of
integers, which are represented internally as 32-bit integers. The
network interface (see \S\ref{sec:network-interface}) will deal with
requests and responses formatted as arrays of 32-bit integers; it is
the responsibility of the marshalling-and-unmarshalling module to
unpack this data into structured representations of core DNS
datatypes.

@@

typedef struct resource_record* resource_record_t;
  \end{lstlisting}
  \caption{Example DNS data structures in our \Kwd{C0} implementation.}\label{fig:c0-data-structures}
\end{figure}

For instance, Figure~\ref{fig:layout-message-header} shows the
bit-level layout of DNS message headers, and
Figure~\ref{fig:layout-resource-record} shows the same for resource
records; Figure~\ref{fig:c0-data-structures} shows how we code these
structures in our \Kwd{C0} implementation. To convert between these
structured representations and the sequences of words which are used
at the boundaries of the network
interface~(\S\ref{sec:network-interface}), we implement functions of
the following kind:

@@

\nocite{willsey-prabhu-pfenning:2016, rfc:1034, rfc:1035}
\bibliographystyle{abbrv}
\bibliography{bibtex-references/refs,project}
